% !TEX root = template.tex

\section{Concluding Remarks}
\label{sec:conclusions}

In this project we put the emphasis in create simple models, with a low number of parameters and that don't need to much time for train it.
Comparing our results with Sainath, Tang we obtained a lower performance, but they create models with hundreds of parameters and also in Tang they only train the models with the small dataset of 65000 instead of 350000.
Therefore, we obtained more simple models with less accuracy but they still competitive in the performance and are very fast to ran and to use in applications.

Besides our expectations and the last research papers about Transformers applied in Computer Vision, our best models where using residuals layer in the models. We believe that the model using Transformer need more tests with different hyper-parameters or only more epochs to see a more competitive result. These kind of models are very fast to train and its motivated to use more epochs to give more time for the model to learn.

\red{This section should take max half a page, I personally find it difficult to come up with really useful observations, I mean ones that bring a new contribution with respect to what you have already expounded in the ``Results'' section. In case you have some serious stuff to write, you may also extend the section to 3/4 of a page :-).}\\

In many papers, here you find a summary of what done. It is basically an abstract where instead of using the present tense you use the past participle, as you refer to something that you have already developed in the previous sections. While I did it myself in the past, I now find it rather useless.\\ 

\MR{\textbf{What I would like to see here is:} 
\begin{enumerate}
\item a very short summary of what done, 
\item some (possibly) intelligent observations on the relevance and {\it applicability} of your algorithms / findings, 
\item what is still missing, and can be added in the future to extend your work.\\
\end{enumerate}
The idea is that this section should be {\it useful} and not just a repetition of the abstract (just \mbox{re-phrased} and written using a different tense...).}\\

\red{\textbf{Moreover:} being a project report, I would also like to see a specific paragraph stating 
\begin{enumerate}
\item[4)] what you have learned, and 
\item[5)] any difficulties you may have encountered.
\end{enumerate}}
