\documentclass[10pt, conference, letterpaper]{IEEEtran}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ansinew]{inputenc} 
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{multirow}
\usepackage{cite}
\usepackage[export]{adjustbox}
\usepackage{breqn}
\usepackage{mathrsfs}
\usepackage{acronym}
%\usepackage[keeplastbox]{flushend}
\usepackage{setspace}
\usepackage{bm}
\usepackage{stackengine}

\usepackage{listings}

\lstset{%
 backgroundcolor=\color[gray]{.85},
 basicstyle=\small\ttfamily,
 breaklines = true,
 keywordstyle=\color{red!75},
 columns=fullflexible,
}%

\lstdefinelanguage{BibTeX}
  {keywords={%
      @article,@book,@collectedbook,@conference,@electronic,@ieeetranbstctl,%
      @inbook,@incollectedbook,@incollection,@injournal,@inproceedings,%
      @manual,@mastersthesis,@misc,@patent,@periodical,@phdthesis,@preamble,%
      @proceedings,@standard,@string,@techreport,@unpublished%
      },
   comment=[l][\itshape]{@comment},
   sensitive=false,
  }

\usepackage{listings}

% listings settings from classicthesis package by
% Andr\'{e} Miede
\lstset{language=[LaTeX]Tex,%C++,
    keywordstyle=\color{RoyalBlue},%\bfseries,
    basicstyle=\small\ttfamily,
    %identifierstyle=\color{NavyBlue},
    commentstyle=\color{Green}\ttfamily,
    stringstyle=\rmfamily,
    numbers=none,%left,%
    numberstyle=\scriptsize,%\tiny
    stepnumber=5,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frameround=ftff,
    frame=single
    %frame=L
}

\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\thesubtable}{\alph{subtable}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptscriptstyle\Delta}}}}

\graphicspath{{./figures/}}
\setlength{\belowcaptionskip}{0mm}
\setlength{\textfloatsep}{8pt}

\newcommand{\eq}[1]{Eq.~\eqref{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\tab}[1]{Tab.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}

\newcommand\MR[1]{\textcolor{blue}{#1}}
\newcommand\red[1]{\textcolor{red}{#1}}
\newcommand{\mytexttilde}{{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}}

%\renewcommand{\baselinestretch}{0.98}
% \renewcommand{\bottomfraction}{0.8}
% \setlength{\abovecaptionskip}{0pt}
\setlength{\columnsep}{0.2in}

% \IEEEoverridecommandlockouts\IEEEpubid{\makebox[\columnwidth]{PUT COPYRIGHT NOTICE HERE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }} 

\title{Small footprint deep neural network architectures for command speech recognition}

\author{María Emilia Charnelli$^\dag$, Lorenti Luciano Rolando$^\dag$
\thanks{$^\dag$Department of Information Engineering, University of Padova, email: \{mariaemilia.charnelli, lucianorolando.lorenti\}@studenti.unipd.it}

} 

\IEEEoverridecommandlockouts

\newcounter{remark}[section]
\newenvironment{remark}[1][]{\refstepcounter{remark}\par\medskip
   \textbf{Remark~\thesection.\theremark. #1} \rmfamily}{\medskip}

\begin{document}

\maketitle

\begin{abstract}

Keyword  spotting  (KWS)  constitutes  a  major  component  of human-technology interfaces. KWS systems enable hands-free speech recognition experience by detecting a trigger phrase used to initiate the interaction with a device. The ubiquity of mobile devices has promoted research of models capable of doing KWS with small memory footprint and low computational power requirements.
In recent years, machine learning techniques, such as deep neural networks, have proven to be useful for keyword spotting. In particular, small footprint models has been proposed using different techniques for  
Residual neural networks (ResNet) and Vision Transformers  (ViT) are recent deep neural network architectures that showed promising results in a broad range of areas. In this context, a comparison between small footpring residual neural network models and ViT was performed. We  analyze  the  effect  of architecture  parameters and the number of trainable parameters of the model. 
The resulting analysis show that ResNet, even with a reduced number of weights can obtain good results with small . while ViT transformer require a bit more carefulyl at the moment of choosing the architeture.
\end{abstract}

\IEEEkeywords
Keyword  spotting, Neural Networks, Vision Transformers, Residual Neural Networks, Recurrent Neural Networks. 
\endIEEEkeywords


\input{report_intro}

\input{related}

\input{model}

\input{results}

\input{conclusions}

\section{Exam rules}

What you need to do to pass the exam:
\begin{itemize}
\item Optional: team up with another student. Max. group size is \textbf{two students} per group;
\item Identify a project to work on, devise your own neural network architecture and test it on the provided dataset;
\item \textbf{Prepare a written project report} including: i) diagrams, ii) configuration pars, iii) results, iv) your discussion;
\item \textbf{Prior to presenting your work}: upload i) your written report and ii) the code;
\item \textbf{Present your work} using slides (max. duration is 20 minutes): take turns in presenting your work, your individual contribution to the project should clearly emerge. Optional: a final and quick demo with running code is appreciated and will be considered in the calculation of the final grade (see below). 
\end{itemize}

Your final grade will be obtained taking into account the following criteria:
\begin{itemize} 
\item \textbf{Project} (60 points): originality (10 pt.) - data preprocessing techniques (10 pt.) - learning architectures (20 pt.) - comparison against other/existing approaches (10 pt.) - live demo of the code (10 pt.)
\item \textbf{Written report} (40 points): clarity of exposition (10 pt.) - completeness (10 pt.) - analysis of results (number and type of metrics used) (20 pt.)
\item \textbf{Oral exposition} (20 points): duration (your talk must take max. 20 minutes, using slides) (10 pt.) - clarity of exposition (10 pt.)
\end{itemize}

The final grade will be computed as
\begin{equation}
\textrm{grade} = \frac{\textrm{tot\_points} \times 30}{110}
\end{equation}

\bibliography{biblio}
\bibliographystyle{ieeetr}

\end{document}


